Paper

### 2020-01-22 Paper.Rmd
paper updates

## Outline
- General Bayesian computational settings
  - Chains
    - Greta
  - Iterations
  - Warmup
  - Thinning
  - initial value specification
- Each sampler
  - BUGS
    - WINE
    - Debugging
  - Jags
  - Nimble
    - Crashes
  - STAN
    - RDS file
  - Greta
- Common coding techniques for each language
  - Truncated normal
  - Specifiying data and constants
  - Matrix multiplication
  - Initial value specification?
  - sigma / tau
- Benchmarking
  - Run time
  - Memory allocation
  - Computational accuracy
  - Benchmarking files
- Folder design
  - General model type
    - Simple conjugate models
    - Regression models
    - Time Series models
    - Survival models
    - 8 Schools
  - Specific model type
  - Scripts for each method 
  - Benchmarking
- Here package
- Models Used

@@

>>>>

## Outline
- General Bayesian computational settings
  - Chains
    - Greta
  - Iterations
  - Warmup
    - STAN/Bugs uses warmup as a part of iterations, Jags/Greta/Nimble have it seperate.
  - Thinning
  - initial value specification
- Each sampler
  - BUGS
    - WINE
    - Debugging
  - Jags
  - Nimble
    - Crashes
  - STAN
    - RDS file
  - Greta
- Common coding techniques for each language
  - Truncated normal
  - Specifiying data and constants
  - Matrix multiplication
  - Initial value specification?
  - sigma / tau
- Benchmarking
  - Run time
  - Memory allocation
  - Computational accuracy
  - Benchmarking files
- Folder design
  - General model type
    - Simple conjugate models
    - Regression models
    - Time Series models
    - Survival models
    - 8 Schools
  - Specific model type
  - Scripts for each method 
  - Benchmarking
- Here package
- Models Used

@@

### Warmup

Since our inferences are based on the assmumption that our draws are from the target distribution, it is wise to discard the samples at the beginning of each chain, since it takes time for the sampler to "settle down". The terms "warmup" and "burn-in" are often used to indicate the number of iterations that we will discard at the beginning of each chain when calculating statistics about our posterior distribution. We can choose this number in the function call for each sampler. In \texttt{OpenBUGS}, \texttt{Nimble}, and \texttt{Jags}, the argument is referred to as burnin, but in \texttt{STAN} and \texttt{Greta} it is called warmup. Some samplers (\texttt{Greta}, \texttt{Jags, Nimble}) treat this warmup argument as a number of iterations to run before starting to track the sampling results, but others (\texttt{STAN}, \texttt{BUGS}) have this be the actual number of iterations to discard out of the total number of specified iterations, so it is important to know which designation a sampler uses.

### Thinning

In some cases, there is high correlation between sequential samples in a given chain, which can bias the resulting posterior inference, which can be diagnosed using some graphical procedures. In this situation, it is wise to "thin" the results by only looking at every ith observation from a chain, such as every 10th observation. While each sampler defaults to including every simulated posterior draw, a user can specify a "thinning rate", which is the rate at which a sampler will keep memory of the observations. A thinning rate of 1 means that every observation will be kept, and a rate of 10 indicates that only every 10th observation will be used.

### Initial Value Specification

In order to start sampling, each Markov chain needs to have an initial value at which to start. These initial values can be either be specified, or can often be randomly generated based on the prior distributions for each parameter of interest. In many cases, it is easiest to have the initial values randomly generated by the sampler. However, in cases where the target distribution is very complex, it is possible that poorly chosen initial values can lead to a chain getting "stuck" in a difficult region, or diverging in the wrong direction. In these cases, a more strategic choice of initial values is advised. \texttt{Nimble} unfortunately requires for these values to be specified instead of randomly generated. Using \texttt{R} to randomly generate the values from the prior distributions can be used in this situation.
